---
title: "What this package does"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What this package does}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753F25hyde)
```

# Overview

Some of the core functions in this package are demonstrated here: tools for regression sums of squares, scatter plots with marginal histograms, overbooking decisions for flights, and visualizing normal tail areas. 

# Total, Model, and Residual Sum of Squares: tssmssrss()

## Description

`tssmssrss()` computes the total, model, and residual sum of squares for a fitted quadratic model and reponse vector. 

## Usage
```
tssmssrss(dataframe, quad.lm, col)
```

### Arguments
`dataframe`  A data frame containing the observed data.  
`quad.lm`    A fitted quadratic regression model of class `lm`.  
`col`        A numeric response vector aligned with `quad.lm`.  

### Value
A numeric vector of length 3 containing `TSS`, `MSS`, and `RSS` in that order.


### Example 

```{r}
quad.lm <- lm(DAMAGE ~ poly(DISTANCE, 2, raw = TRUE), data = fire)
tssmssrss(fire, quad.lm, fire$DAMAGE)
```

# Scatter Plot with Marginal Histograms: scatterhist()

## Description

`scatterhist()` creates a scatter plot of two quantitative variables with marginal histograms for a quick look at joint and marginal behavior.

## Usage
```
scatterhist(x, y, xlab = "", ylab = "")
```

### Arguments
`x`     A numeric vector for the x-axis.  
`y`     A numeric vector for the y-axis.  
`xlab`  Character label for the x-axis.  
`ylab`  Character label for the y-axis.  

### Value
A scatter plot of `x` versus `y` with histograms shown along the margins.

### Example

```{r}
scatterhist(fire$DISTANCE, fire$DAMAGE,
            xlab = "Distance", ylab = "Damage")
```

# Optimal Number of Tickets: ntickets()

## Description

`ntickets()` finds how many tickets to sell given an acceptable overbooking probability.

## Usage
```
ntickets(N, gamma, p)
```

### Arguments
`N`      Number of seats available on the flight.  
`gamma`  Acceptable probability of overbooking (risk tolerance).  
`p`      Probability that each individual ticket holder shows up.  

### Value
A named list containing the discrete solution `nd`, the continuous solution `nc`, and the inputs `N`, `p`, and `gamma`.

### Example

```{r}
ntickets(400, gamma = 0.02, p = 0.95)
```

# Normal Curve Visualization: myncurve()

## Description

`myncurve()` shades the left tail of a normal curve and returns the probability $P(X \le a)$.

## Usage
```
myncurve(mu, sigma, a)
```

### Arguments
`mu`     Mean of the normal distribution.  
`sigma`  Standard deviation of the normal distribution (positive).  
`a`      Cutoff value defining the left-tail area.  

### Value
A named list containing `mu`, `sigma`, `a`, and `area`, where `area = P(X <= a)` under the specified normal distribution.

### Example

```{r}
myncurve(mu = 25, sigma = 5, a = 20)
```



